Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-01-15 TEBenchmarkPaper/article.tex
Don't talk about Isabelle if/until we include IsaCoSy

\begin{itemize}
\item For each problem, there should be a clear distinction between the theorem
  to be proved and the definitions involved, such that the two can be easily and
  meaningfully separated. This rules out problem sets like those of
  SMT-COMP~\cite{barrett2005smt}, where many problems involve uninterpreted
  functions, whose behaviour is \emph{implicit} in the logical structure of the
  theorem statement but not separately \emph{defined}.
\item Definitions should be \emph{strongly typed}, such that they can be
  translated into the native language of each ATE system (in this work, those
  languages are Haskell and Isabelle).
\item The problem set should be relevant to the desired domain. In our case, we
  desire higher-order functions and inductively defined types, which rules out
  first-order languages/logics (such as TPTP~\cite{sutcliffe2009tptp}).
\item Since it will act as our ground truth, the problem set should ideally
  contain every ``interesting'' conjecture involving its included
  definitions. Realistically, we should aim for each definition to appear in
  \emph{many} theorem statements; rather than each problem having unique
  definitions.
\item The problem set should be as large as possible, for robustness of the
  resulting statistics.
\end{itemize}

>>>>

\begin{itemize}
\item For each problem, there should be a clear distinction between the theorem
  to be proved and the definitions involved, such that the two can be easily and
  meaningfully separated. This rules out problem sets like those of
  SMT-COMP~\cite{barrett2005smt}, where many problems involve uninterpreted
  functions, whose behaviour is \emph{implicit} in the logical structure of the
  theorem statement but not separately \emph{defined}.
\item Definitions should be \emph{strongly typed}, such that they can be
  translated into the native language of each ATE system (in this work, that
  includes Haskell\iffalse FIXME and Isabelle\fi).
\item The problem set should be relevant to the desired domain. In our case, we
  desire higher-order functions and inductively defined types, which rules out
  first-order languages/logics (such as TPTP~\cite{sutcliffe2009tptp}).
\item Since it will act as our ground truth, the problem set should ideally
  contain every ``interesting'' conjecture involving its included
  definitions. Realistically, we should aim for each definition to appear in
  \emph{many} theorem statements; rather than each problem having unique
  definitions.
\item The problem set should be as large as possible, for robustness of the
  resulting statistics.
\end{itemize}
